Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2020-10-13 paper/paper.Rmd
delete previuos section on data collection

Our main hypothesis is about the incoporation of variance in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal. How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal. We explored the effects of individual differences in movement by modifying our base simulation, in which the probability density function used to model animal movement was different between populations or a subcategory. In simulations at the population level, we used a single pdf to sample step sizes from, while for individual and family level simulations we used multiple pdfs to sample step sizes from, where each pdf was associated to a specific individual or family group.

Commonly used probability distributions for sampling the animal movement step size included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008]. These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.

### Data collection/manipulation

@@

We used subsequent animal locations to estimate distance moved in a given tracking session, then calculated movement rates per minute for each movement bout. We defined a movement bout as the movement occurring between two consecutive GPS locations. *Is this ok? not sure how to describe how I considered this* We generated a distribution of movement rates and selected the animals that had a minimum of 30 observations giving us a dataset with information on twelve individual birds. Unlike previous work by Holbrook [-@holbrook_home_2011] we restricted our analysis to consecutive locations only, to better capture variation in trajectory and movement rates in meters per minute for a given flight session. We were not focused on distance to origin from the animal’s perspective, but on movement bouts in a continuous tracking session, in order to estimate trajectory movement, which would directly influence the distance that seeds get dispersed from a focus tree.

>>>>

Our main hypothesis is about the incoporation of variance in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal. How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal. We explored the effects of individual differences in movement by modifying our base simulation, in which the probability density function used to model animal movement was different between populations or a subcategory. In simulations at the population level, we used a single pdf to sample step sizes from, while for individual and family level simulations we used multiple pdfs to sample step sizes from, where each pdf was associated to a specific individual or family group. The pdf for the population level is f(x, sigma), where sigma is the parameters for population, and fx(x, sigma_vector), is for the individual or family level and sigma vector represents a vector of parameters for the pdf, where each parameter corresponds to a different individual or family group. We used four different pdfs for our simulations based on used probability distributions for sampling the animal movement step size including an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008]. These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size. We also performed a mixed distribution simulation at the individual and population levels, where each individual or family group would not only have their specific set of parameter estimates, but we also allowed for variaiton in the structure of the pdf. Here I should write out how it looks mathematically.

## Data collection/manipulation

@@
